\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{amsmath,graphicx}
\usepackage{verbatim}
\newcommand{\para}[1]{\noindent\textbf{#1}}
\def\x{{\mathbf x}}
\def\L{{\cal L}}
\newcommand{\comments}[1]{}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Training semantic segmentation networks with temporal consistency}
%\title{Semi-supervised learning for semantic segmentation}
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in %Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
%}

\author{\IEEEauthorblockN{1\textsuperscript{st} Feiyu Qin}
\IEEEauthorblockA{\textit{University of Science and Technology of China}\\
Heifei, China \\
feiyuqin@mail.ustc.edu.cn}
\and
%\IEEEauthorblockN{2\textsuperscript{nd} Lumeng Cao}
%\IEEEauthorblockA{\textit{University of Science and Technology of China}\\
%	Heifei, China \\
%	clm@mail.ustc.edu.cn}
%\and
\IEEEauthorblockN{2\textsuperscript{rd} Xuejin Chen}
\IEEEauthorblockA{\textit{University of Science and Technology of China}\\
	Heifei, China \\
	xjchen99@ustc.edu.cn}
}
\maketitle
\input{Abstract.tex}
\input{Introduction.tex}
\input{methodology.tex}
\input{Experiments.tex}
\input{Conclusion.tex}

\bibliographystyle{IEEEbib}
\bibliography{strings,refs}


\comments{
\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
}
\end{document}
